Supplementary material for "Hack Weeks as a model for Data Science Education and Collaboration"

### 2018-06-06 supplementary_material.tex
Fixed newly introduced typo

For no combination of question questions with a demographic variable, do we ﬁnd a $p$-value below the trial-corrected signiﬁcance threshold of $p < 0.0007$ quoted in Section \ref{sec:suppmaterials}. In the main text, we place these null results in context, and refer to the tests that were near significance, and were coupled with a moderate to large effect size, as an indication of where future research may be fruitful. The results also discuss the present study's limitations.

>>>>

For no combination of questions with a demographic variable, do we ﬁnd a $p$-value below the trial-corrected signiﬁcance threshold of $p < 0.0007$ quoted in Section \ref{sec:suppmaterials}. In the main text, we place these null results in context, and refer to the tests that were near significance, and were coupled with a moderate to large effect size, as an indication of where future research may be fruitful. The results also discuss the present study's limitations.
